Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-19 doc/manuscript/ESSDmanuscript.Rmd
finished description of mapping land classification

*(now describe sub-category classification, which depends on past land use)*

Documented at https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/defining_land_subcategory.md, https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/IPCC_LandUse_mapping.csv, and in [issue #8](https://github.com/forc-db/IPCC_database_integration/issues/8).

>>>>

Classification into sub-categories was dependent upon stand age and site history (section `r  section_land_use_categories`).
For Forest Land ≥ 20 years old or of unknown (relatively mature) age, or Forest Land < 20 years old that was forest prior to a stand-clearing disturbance, the past land-use category was Forest Land, making the sub-category "Forest Land Remaining Forest land".
For forests <20 years old with history including cultivation/ tillage or grazing, past land-use categories were Cropland and Grassland, respectively, making land-use subcategories were "Cropland converted to Forest Land" and "Cropland converted to Forest Land", respectively.
For forests <20 years old with unspecified previous agricultural use, we assigned the sub-category "Land Converted to Forest land".
Forests <20 years old with unknown land use prior to the study date were simply classified as "Forest Land".
The same logic was applied for savannas, but including both Forest Land and Grassland as potentially relevant categories.

### 2022-04-19 doc/manuscript/ESSDmanuscript.tex
finished description of mapping land classification

\emph{(now describe sub-category classification, which depends on past
land use)}

Documented at
https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB\_mapping/defining\_land\_subcategory.md,
https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB\_mapping/IPCC\_LandUse\_mapping.csv,
and in
\href{https://github.com/forc-db/IPCC_database_integration/issues/8}{issue
\#8}.

>>>>

Classification into sub-categories was dependent upon stand age and site
history (section 2.2). For Forest Land ≥ 20 years old or of unknown
(relatively mature) age, or Forest Land \textless{} 20 years old that
was forest prior to a stand-clearing disturbance, the past land-use
category was Forest Land, making the sub-category ``Forest Land
Remaining Forest land''. For forests \textless20 years old with history
including cultivation/ tillage or grazing, past land-use categories were
Cropland and Grassland, respectively, making land-use subcategories were
``Cropland converted to Forest Land'' and ``Cropland converted to Forest
Land'', respectively. For forests \textless20 years old with unspecified
previous agricultural use, we assigned the sub-category ``Land Converted
to Forest land''. Forests \textless20 years old with unknown land use
prior to the study date were simply classified as ``Forest Land''. The
same logic was applied for savannas, but including both Forest Land and
Grassland as potentially relevant categories.
